Blowship - Untraceable Instantaneous Message Transfer via a Central Server

### 2014-03-15 paper.tex
Figure
Meow

\subsection{Peer Discovery}
Unfortunately, if peers discover eachother through Surge, he could ensure that any peer only knows about compromised peers (Effectively making $\phi = 1$).

@@

We solve this problem as follows:

>>>>

\subsection{Peer Discovery}
Having a central server could make peer discovery much more efficient. Unfortunately, if peers discover eachother through Surge, he could ensure that any peer only knows about compromised peers (Effectively making $\phi = 1$).

@@

We maintain the efficiency of a central directory server while
